---
title: "Mini-Project 2"
author: "Julianna Alvord and Peyton Draper"
date: "October 31, 2017"
output: html_document
---


## Loading the data

This project is so interesting and relevant to my life! merpy derpy

```{r, include = FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r}
library(tidyverse)
library(scales)

join1 <- contributions %>%
  inner_join(committees, by = "cmte_id") %>%
<<<<<<< HEAD
  select("cmte_id", "cmte_dsgn", "cmte_type", "cmte_name",  "cmte_party_affiliation", "org_type", "transaction_type", "transaction_amt") %>%
  filter(cmte_party_affiliation %in% c("DEM", "REP")) %>%
  arrange(desc(transaction_amt))

join2 <- house_elections %>%
  inner_join(candidates, by = c("fec_id" = "cand_id")) %>%
  select("fec_id", "state", "district", "incumbent", "candidate_name", "cand_party_affiliation", "primary_votes", "runoff_votes", "general_votes", "ge_winner")

join1plot <- join1 %>%
  ggplot(aes(x = cmte_party_affiliation, y = transaction_amt)) +
  geom_point() +
  scale_x_discrete(name = "Party Affiliation") +
  scale_y_continuous(name = "Transaction Amount", labels = dollar)

join1plot
```
=======
  select("cmte_id", "cmte_dsgn", "cmte_type", "cmte_party_affiliation", "org_type", "transaction_type", "transaction_amt", "entity_type", "connected_org_name")

# join2 <- join1 %>%
#   filter(cmte_party_affiliation %in% c("DEM", "REP")) %>%
#   group_by(cmte_party_affiliation) %>%
#   summarise(avg_transaction = mean(transaction_amt), total_transaction = sum(transaction_amt)) %>%
#   mutate(avg_transaction_as_int = readr::parse_number(avg_transaction))
# 
# join3 <- join1 %>%
#   filter(cmte_party_affiliation %in% c("DEM", "REP")) %>%
#   group_by(cmte_party_affiliation) %>%
#   summarise(total_transaction = sum(transaction_amt))
# 
# ggplot(join2, aes(x = cmte_party_affiliation, y = avg_transaction_as_int)) +
#   geom_point()
```


```{r}
# house_elections <- house_elections %>%
#   group_by(state) %>%
#   summarise(total_votes = sum(primary_votes))
# 
# contributions <- contributions %>%
#   group_by(state) %>%
#   summarise(total_contr = sum(transaction_amt))


```

```{r}
# join_house_cand <- house_elections %>%
#   inner_join(candidates, by = c("fec_id" = "cand_id"))


```

>>>>>>> d1431684f0c8ddba889a49d41d05f218f3020793
